Lessons Learned for JWST Transiting Planet Time Series from Ground-based Studies of the NIRCam Detectors

### 2018-12-25 ms.tex
added amplifier offsets as another potential systematic.
corrected int times and int starts of long dark time series.

Known detector effects that could affect stability include:
\begin{itemize}[noitemsep]
	\item \textbf{Intrapixel sensitivity:} - including sub-pixel flat fielding issues and sub-pixel crosshatching on the detectors \citep{shapiro2018crosshatch}
	\item \textbf{Pre-amp reset offsets:} (an Asic-related effect) 
The resets cause discontinuities in the pedestal level of all pixels between frames. This is an effect where averaging over more pixels does not decrease the noise, but reference pixel or background subtraction can. These are discussed in Section \ref{sec:preAmp}.
	\item \textbf{1/f noise:} This is a noise source where most of the noise power is concentrated as low frequencies. 1/f noise causes spatial correlations in the fast-read direction (along detector rows). It is highly correlated between amplifiers, suggesting that it is caused by a common reference voltage. 1/f noise is efficiently removed by reference pixels
	\item \textbf{Even/odd offsets:} Alternating columns have different bias levels. Additionally, there are offsets between columns that can change from frame to frame, especially on NIRCam's LW detector
	\item \textbf{kTC noise:} A random process due to the unknown amount of charge stored at the reset voltage level
	\item \textbf{Detector Temperature Fluctuations:} The JWST detectors are sensitive to temperature changes on the detectors. For example, laboratory tests show that 100 mK temperature fluctuations can result in $\sim$ 80 ADU changes on the detector that are not corrected by reference pixels \citep{hall2005jwstArrays}. Fortunately, the detectors are actively thermally controlled to keep the temperature fluctuations to $\lesssim$ 1 mK.
	\item \textbf{ASIC Temperature Fluctuations:} The asic temperature will change as the operating mode. For example, in the CV3 stability test, the temperature of the A asic changed by $\sim$80 mK when the readout mode was switched from full frame to subarray. This temperature change is expected to be smaller in flight due to adjustments in ?? (Marcia said in 2018-11-02 meeting)
	\item \textbf{Elevated Columns} There is correlated noise along a column in many frames. These elevated columns can sometimes even move with time.
	\item \textbf{Random Telegraph Noise (RTN)} Some of the pixels will exhibit spontaneous changes jumps in signal even with no illumination. Fortunately, RTN appears in only $\sim$1000 pixels out of 4$\times 10^6$ on the array.
	\item \textbf{Detector Fringing} \textbf{\textcolor{red}{Add more details and citations}} The thin $\sim 5\mu$m layers of the H2RG detectors will cause interference patterns on the array due to constructive and destructive interference of light at wavelengths similar to the thickness of the layers. If the detector fringe pattern changes with time, it will change the throughput of a grism image.
\end{itemize}

@@

@@

\begin{figure}[!hbtp]
\centering
\includegraphics[width=.5\columnwidth]{subarray_config_tser.pdf}
\caption{A variety of subarrays in the OTIS stability tests organized by increasing number of pixels (and decrease number of groups up the ramp).
The standard deviation decreases as the number of groups up the ramp becomes more numerous.}\label{fig:OTISsubarrays}
\end{figure}

>>>>

Known detector effects that could affect stability include:
\begin{itemize}[noitemsep]
	\item \textbf{Intrapixel sensitivity:} - including sub-pixel flat fielding issues and sub-pixel crosshatching on the detectors \citep{shapiro2018crosshatch}
	\item \textbf{Pre-amp reset offsets:} (an Asic-related effect) 
The resets cause discontinuities in the pedestal level of all pixels between frames. This is an effect where averaging over more pixels does not decrease the noise, but reference pixel or background subtraction can. These are discussed in Section \ref{sec:preAmp}.
	\item \textbf{1/f noise:} This is a noise source where most of the noise power is concentrated as low frequencies. 1/f noise causes spatial correlations in the fast-read direction (along detector rows). It is highly correlated between amplifiers, suggesting that it is caused by a common reference voltage. 1/f noise is efficiently removed by reference pixels
	\item \textbf{Even/odd offsets:} Alternating columns have different bias levels. Additionally, there are offsets between columns that can change from frame to frame, especially on NIRCam's LW detector
	\item \textbf{kTC noise:} A random process due to the unknown amount of charge stored at the reset voltage level
	\item \textbf{Detector Temperature Fluctuations:} The JWST detectors are sensitive to temperature changes on the detectors. For example, laboratory tests show that 100 mK temperature fluctuations can result in $\sim$ 80 ADU changes on the detector that are not corrected by reference pixels \citep{hall2005jwstArrays}. Fortunately, the detectors are actively thermally controlled to keep the temperature fluctuations to $\lesssim$ 1 mK.
	\item \textbf{ASIC Temperature Fluctuations:} The asic temperature will change as the operating mode. For example, in the CV3 stability test, the temperature of the A asic changed by $\sim$80 mK when the readout mode was switched from full frame to subarray. This temperature change is expected to be smaller in flight due to adjustments in ?? (Marcia said in 2018-11-02 meeting)
	\item \textbf{Elevated Columns} There is correlated noise along a column in many frames. These elevated columns can sometimes even move with time.
	\item \textbf{Random Telegraph Noise (RTN)} Some of the pixels will exhibit spontaneous changes jumps in signal even with no illumination. Fortunately, RTN appears in only $\sim$1000 pixels out of 4$\times 10^6$ on the array.
	\item \textbf{Detector Fringing} \textbf{\textcolor{red}{Add more details and citations}} The thin $\sim 5\mu$m layers of the H2RG detectors will cause interference patterns on the array due to constructive and destructive interference of light at wavelengths similar to the thickness of the layers. If the detector fringe pattern changes with time, it will change the throughput of a grism image.
	\item \textbf{Amplifier Boundary Discontinuities} 
\end{itemize}

@@

\subsection{Amplifier Boundary Discontinuities}
\begin{figure}[!hbtp]
\centering
\includegraphics[width=.99\columnwidth]{amplifier_offsets_in_otis_lw_grism.pdf}
\caption{An example slope image from the LW OTIS Stability test.
No reference pixel correction is applied, leaving offsets at the amplifier boundaries.}\label{fig:ampOffsetsOtisGrismSlope}
\end{figure}

@@

\begin{figure}[!hbtp]
\centering
\includegraphics[width=.5\columnwidth]{subarray_config_tser.pdf}
\caption{A variety of subarrays in the OTIS stability tests were read out with similar integration times (32 to 39 seconds) to compare relative precision of the read modes. 
The time series are ordered vertically in increasing frame duration (and decreasing number of groups up the ramp) toward the bottom.
The standard deviation decreases as the number of groups up the ramp becomes more numerous.}\label{fig:OTISsubarrays}
\end{figure}
